Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-12 Dissertation/Defense/defense.tex
did patrol, started experiments, need to go back and add ogm of hallway & Mars figs

\begin{itemize}
	\item Bayesian Framework
	\begin{itemize}
	\item Markov Assumption: latest a priori cell occupancy probabilities capture the information from all prior observations
	\item Log-Odds Ratio: popular representation due to simple additive update structure and probability truncation avoidance, but requires the \emph{assumption}
	\begin{align*}
		P(Z_t|\mathbf{m}_i,X_{1:t},Z_{1:t-1})\approx P(Z_t|\mathbf{m}_i,X_t)
	\end{align*}
	\end{itemize}
\vspace*{0.0cm}\pause
	\item Inverse Sensor Model
	\begin{align*}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}\sum_{m\in\mathcal{M}_i}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}).
\end{align*}
	\begin{itemize}
	\item Given $n$ grid cells: $\mathcal O(2^n)$ is \emph{computationally intractable}, motivating a different solution
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item Multiple agents can accomplish tasks faster and more reliably than a single agent
	\item Large groups are capable of coverage in large environments
	\item Problem: multi-vehicle map information gain optimality can be computationally intractable
	\item Solution: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
\end{itemize}

@@

\begin{itemize}
\item Central executive completes $n$ auctions for $n$ robots
\begin{enumerate}
	\item Each robot determines its optimal future pose, and bids the objective function
	\item The winner is awarded this future pose, and the remaining robots update their bids according to
	\begin{itemize}
		\item New expected map changes from the winner
		\item Collision-avoidance with the winner
	\end{itemize}
	\item Repeat these steps with the remaining robots
\end{enumerate}
\item The efforts are coordinated by updating bids between auctions
\end{itemize}
\end{frame}

@@

@@

>>>>

\begin{itemize}
	\item Bayesian Framework
	\begin{itemize}
	\item Markov Assumption: latest a priori cell occupancy probabilities capture the information from all prior observations
	\item Log-Odds Ratio: popular representation due to simple additive update structure and probability truncation avoidance, but requires the \emph{assumption}
	\begin{align*}
		P(Z_t|\mathbf{m}_i,X_{1:t},Z_{1:t-1})\approx P(Z_t|\mathbf{m}_i,X_t)
	\end{align*}
	\end{itemize}
\vspace*{0.0cm}\pause
	\item Inverse Sensor Model
	\begin{align*}
&P(\mathbf{m}_i|z_{t,l},X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l}\sum_{m\in\mathcal{M}_i}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}).
\end{align*}
	\begin{itemize}
	\item Given $n$ grid cells: $\mathcal O(2^n)$ is \emph{computationally-intractable}, motivating a different solution
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item Multiple agents can accomplish tasks faster and more reliably than a single agent
	\item Large groups are capable of coverage in large environments
	\item Problem: multi-vehicle map information gain optimality can be computationally-intractable
	\item Solution: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
\end{itemize}

@@

\begin{itemize}
\item Central executive completes $n$ auctions for $n$ robots
\begin{enumerate}
	\item Each robot determines its optimal future pose, and bids the objective function
	\item The winner is awarded this future pose, and the remaining robots update their bids according to
	\begin{itemize}
		\item New expected map changes from the winner
		\item Collision-avoidance with the winner
	\end{itemize}
	\item Repeat these steps with the remaining robots
\end{enumerate}
\item The efforts are coordinated by updating bids between auctions
\item The algorithm follows a receding-horizon framework: future pose optimization repeats as quickly as possible
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Cooperative Autonomous Patrol}

\begin{itemize}
	\item Existing Approaches
	\begin{itemize}
		\item Rely on a known map and use Voronoi diagrams to disperse
		\item Another approach introduces cell periodicity: observe long-term dynamics of objects at the same location on the occupancy grid
		\item Bio-inspired approach uses digital pheromones 
		\item Minimizing robot idleness
	\end{itemize}
	\item Proposed Approach
	\begin{itemize}
		\item Degrade occupancy grid cells toward their initial values with exponential decay
		\item Only affects existing probability values without new variables to track
		\item Promotes exploration first, then patrol
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Continuous-Time Markov Process}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{markov_diagram_continuous.pdf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{DegradeExamples.pdf}
\end{figure}

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
%  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

\begin{frame}
\frametitle{Multi-Vehicle Autonomous Exploration and Patrol Conclusions}

\begin{itemize}
	\item Robotic tasks are assigned following a bidding-based framework to avoid a computationally-intractable solution
	\item Only one robot wins an auction, and bids are updated for the remaining robots in subsequent auctions
	\item A receding-horizon framework optimizes the time to update the optimal future poses
	\item Cell degradation provides a simple means for autonomous patrol via a continuous-time Markov process
	\item Numerical examples of a large experimental space demonstrate both algorithms
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Experimental Overview}

\begin{enumerate}
	\item Ground vehicle experiment for 2D occupancy grid mapping and autonomous exploration
	\item Flying vehicle experiment in large 3D space resembling an office
	\item Flying vehicle experiment in a complex 3D space
\end{enumerate}
\end{frame}

### 2018-07-12 Dissertation/Thesis/tex/ae2D.tex
increased refs from 42 to 61 excluding geometric control ones, which will be added later
did patrol, started experiments, need to go back and add ogm of hallway & Mars figs

There are two important steps to moving a robot on a collision-free trajectory to its optimal pose. First, Dijkstra's algorithm~\cite{Dij59} provides the cost map and optimal collision-free waypoints. Then, a constrained polynomial least squares trajectory serves as the desired path, which is followed by a controller.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.4\textwidth]{intel_clean.png}
	\caption{Intel Research Lab Floor Plan Benchmark~\cite{kummerle2009measuring}.}
	\medskip
	\small
	The 2D floor plan from the Intel Research Lab is simplified to eliminate small objects. The remaining black pixels are used to produce walls for 2D simulations.
\label{fig:intel}
\end{figure}

>>>>

There are two important steps to moving a robot on a collision-free trajectory to its optimal pose. First, Dijkstra's algorithm~\cite{Dij59,Dij11} provides the cost map and optimal collision-free waypoints. Then, a constrained polynomial least squares trajectory serves as the desired path, which is followed by a controller.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.4\textwidth]{intel_clean.png}
	\caption{Intel Research Lab Floor Plan Benchmark}
	\medskip
	\small
	The 2D floor plan from the Intel Research Lab~\cite{kummerle2009measuring} is simplified to eliminate small objects. The remaining black pixels are used to produce walls for 2D simulations.
\label{fig:intel}
\end{figure}

### 2018-07-12 Dissertation/Thesis/tex/multivehicle.tex
did patrol, started experiments, need to go back and add ogm of hallway & Mars figs

\begin{figure}
\centering
\includegraphics[width=\textwidth]{markov_diagram_continuous.pdf}
\caption{The continuous-time Markov process for a single binary cell occupancy is illustrated. As time progresses, this process degrades the cell slowly toward $P_\infty.$}
\label{fig:MarkovDegradeContinuous}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{markov_diagram_continuous.pdf}
\caption{Continuous-Time Markov Process Illustration}
\medskip
\small
The continuous-time Markov process for a single binary cell occupancy is illustrated. As time progresses, this process degrades the cell slowly toward $P_\infty.$
\label{fig:MarkovDegradeContinuous}
\end{figure}
